Comparative Evaluation of Spark and Flink Stream Processing

### 2017-02-21 paper/paper.tex
added sector change detetcion workload

\subsection{Workloads Design}
In our experimental evaluation, we developed two streaming processing workloads that read the ADS-B messages stream from Kafka to perform basic trajectories analysis methods. In our design choice, we try to cover key main points related to the streaming processing, to evaluate how  does each framework perform. The following are general key aspects of  streaming data processing were covered by our workloads design:

@@

\end{itemize}
\subsection{Workloads Implementation}
\section{Performance Results}

>>>>

\subsection{Evaluation Workloads}
In our experimental evaluation, we developed two streaming processing workloads that read the ADS-B messages stream from Kafka to perform basic trajectories analysis methods. In our design choice, we try to cover key main points related to the streaming processing, to evaluate how  does each framework perform. The following are general key aspects of  streaming data processing were covered by our workloads design:

@@

\end{itemize}

\subsubsection{Sector of Trajectory Change Detection}

The goal of sector change detection workload is to detect the  enter or leaving of aircraft from one air sector to other, by processing the trajectories stream. Given that the dataset of sectors (i.e., polygons) available as reference to  check against it, also it used to assign the corresponding sector for certain aircraft position. In this workload, providing the  global model of data (sectors dataset) in streaming processing workload is tested.Moreover, preserving the stream records order and parallel streams consuming are covered.

\section{Performance Results}
